Technical Report

### 2018-04-10 fully-abstract-comp/technical-report.tex
Clarify phrase structure.

\begin{definition}[Plugging a program into a context]
  When $\var{comp'}$ is a context for component $\var{comp}$, $\var{comp}' \bowtie \var{comp} \rightsquigarrow \Phi$.
  Then we write $\plug{\var{comp'}}{\var{comp}}$ for the execution configuration $\Phi$.
\end{definition}

>>>>

\begin{definition}[Plugging a program into a context]
  When $\var{comp'}$ is a context for component $\var{comp}$ and $\var{comp}' \bowtie \var{comp} \rightsquigarrow \Phi$, 
  then we write $\plug{\var{comp'}}{\var{comp}}$ for the execution configuration $\Phi$.
\end{definition}
